Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-12-11 paper/ms.tex
new small changes

Figure \ref{fig:correlation_parameters} shows the main results for the
best estimates of $\theta_{0}-\beta$ in the parameterization of the
ACF. Blue circles with error bars represent the results from the mocks
and the horizontal line the result from observations reported by
\cite{Ouchi2010} over a field with average number density. The
observational result does not have an uncertainty associated with
$\beta$ because the parameter was fixed in the fit. Only $40$ models
are consistent with the new constraints.

Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the selected models
models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm
  min}$-$f_{\rm occ}$. To make this selection we consider that
a model is consistent with observations if there is a $1$-$\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. Comparing this Figure
\ref{fig:restriction_mock_and_f_occ_corr} with the results shown in Figure
\ref{fig:restriction_mock} we see that the new constraint disfavors
practically all models with $M_{\rm max}>10^{12}$.

Our main conclusions after this comparison is that clustering
information is able to put meaningful constraints on the values of
$M_{\rm max}$. However, the possible values for the occupation
fraction, despite having a strong correlation with $M_{\rm min}$
remain unconstrained.

>>>>

Figure \ref{fig:correlation_parameters} shows the main results for the
best estimates of $\theta_{0}-\beta$  used in the ACF parameterization. 
Blue circles with error bars represent the theoretical results
and the horizontal line the observations by \cite{Ouchi2010} over a
field with average number density. The  observational result does not
have an uncertainty associated with $\beta$ because the parameter was
fixed in the fit.

Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the selected models
models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm
  min}$-$f_{\rm occ}$. To make this selection we consider that
a model is consistent with observations if there is a $1$-$\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$.  We find that $40$ models are consistent with the ACF
constraints.

Comparing Figure
\ref{fig:restriction_mock_and_f_occ_corr} with Figure
\ref{fig:restriction_mock} we see that the new constraint disfavors
almost all models with $M_{\rm max}>10^{12}$. The only exception is 
a narrow range of models with $M_{\rm min}=10^{10.9}$, however, we
have verified that these models are only marginally consistent witht
the ACF constraints in the $\theta_0$-$\beta$ plane.

From this comparison we conclude that clustering  information is able
to put meaningful constraints on the values of $M_{\rm max}$, but not
on he occupation fraction.
